Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-10-02 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
update scale-behavioral correlation analysis for rep-exp

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}

# clean data for trad. analysis
df.M1 <- df.M
df.C1 <- df.C
df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

>>>>

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# clean data for trad. analysis
df.M1 <- df.M
df.C1 <- df.C
df.M1$RT <- df.M1$RT * 1000 # transfer from seconds to min seconds
df.C1$RT <- df.C1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

```{r preproc questionnair,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# load the data
df.quest1 <- read.csv("exp7_rep_Q4.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) %>%
      filter(session == 1)
df.quest2 <- read.csv("exp7_rep_Q5.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE) %>%
      filter(session == 1)
df.quest <- merge(df.quest1,df.quest2,by = "subjID")
# calculate the reliability of each questionnair
# get the name and key for each scale
slfEsteemNames <- c( "slfEsteem_1", "slfEsteem_2", "slfEsteem_3", "slfEsteem_4", "slfEsteem_5",
                     "slfEsteem_6", "slfEsteem_7", "slfEsteem_8", "slfEsteem_9", "slfEsteem_10")
slfEsteemKeys  <- c(1,2,-3,4,-5,6,7,-8,-9,-10)        # for current dataset
slfEsteemKeys2 <- c( "slfEsteem_1", "slfEsteem_2", "-slfEsteem_3", "slfEsteem_4", "-slfEsteem_5",
                     "slfEsteem_6", "slfEsteem_7", "-slfEsteem_8", "-slfEsteem_9", "-slfEsteem_10")
slfEsteemAlpha <- psych::alpha(df.quest[,slfEsteemNames],keys = slfEsteemKeys) # alpha
print(slfEsteemAlpha$total[2]) # 0.8593
slfEsteemOmega <- psych::omega(df.quest[,slfEsteemNames]) # omega 0.7455 0.9341
print(c(slfEsteemOmega$omega_h,slfEsteemOmega$omega.tot))

# calculate the score for the trait self-esteem
slfEsteemScore <- psych::scoreItems(slfEsteemKeys2,df.quest[,slfEsteemNames], totals = F, min = 1, max = 4)
df.quest$slfEsteem <- slfEsteemScore$scores

# calculate for moral identity
moralIdNames <- c("MoralId_1","MoralId_2","MoralId_3","MoralId_4","MoralId_5","MoralId_6",
                  "MoralId_7","MoralId_8","MoralId_9","MoralId_10","MoralId_11","MoralId_12",
                  "MoralId_13","MoralId_14","MoralId_15")
moralIdKeys <- c(1,2,3,4,-5,6,7,8,9,10,11,12,13,14,15)

moralIdAlpha <- psych::alpha(df.quest[,moralIdNames],keys = moralIdKeys) # alpha
print(moralIdAlpha$total[2]) # 0.9178
moralIdOmega <- psych::omega(df.quest[,moralIdNames]) # omega 0.7583 0.9454
print(c(moralIdOmega$omega_h,moralIdOmega$omega.tot))

moralIdinNames <- c("MoralId_1","MoralId_2","MoralId_5","MoralId_8","MoralId_10",
                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
moralIdinKeys <- c(1,2,-3,4,5,6,7,8,9)
moralIdinKeys2 <- c("MoralId_1","MoralId_2","-MoralId_5","MoralId_8","MoralId_10",
                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
moralIdinAlpha <- psych::alpha(df.quest[,moralIdinNames],keys = moralIdinKeys) # alpha
print(moralIdinAlpha$total[2]) # 0.8884
moralIdinOmega <- psych::omega(df.quest[,moralIdinNames]) # omega 0.7115 0.939
print(c(moralIdinOmega$omega_h,moralIdinOmega$omega.tot))

# caculate the score for internal moral identity
moralIdinScore <- psych::scoreItems(moralIdinKeys2,df.quest[,moralIdinNames], totals = F, min = -2, max = 2)
df.quest$moralIdinScore <- moralIdinScore$scores

moralIdexNames <- c("MoralId_3","MoralId_4","MoralId_6",
                  "MoralId_7","MoralId_9","MoralId_15")
moralIdexKeys <- c(1,2,3,4,5,6)
moralIdexAlpha <- psych::alpha(df.quest[,moralIdexNames],keys = moralIdexKeys) # alpha
print(moralIdexAlpha$total[2]) # 0.844
moralIdexOmega <- psych::omega(df.quest[,moralIdexNames]) # omega 0.684 0.91
print(c(moralIdexOmega$omega_h,moralIdexOmega$omega.tot))

# calculate the score for external moral identity
moralIdexScore <- psych::scoreItems(moralIdexNames,df.quest[,moralIdexNames], totals = F, min = -2, max = 2)
df.quest$moralIdexScore <- moralIdexScore$scores

# find the intersection between behavioral data and questionnarie data.
tmp <- merge(df.v.sum_eff_all_w,df.quest[,c("subjID","slfEsteem","moralIdinScore","moralIdexScore")],by.x = "Subject",by.y = "subjID",all = TRUE)
tmp <- tmp[complete.cases(tmp),]

# write files to an upper-level folder
setwd(traDir)
write.csv(tmp,'MS_cross_taskeffect_wide_w_scale.csv',row.names = F)
setwd(curDir)

# load data from exp1
crossf_effect_scale_1 <- read.csv("D:\\HCP_cloud\\Exps\\P1_Pos_Self\\Exp_Behav_Moral_Asso\\Exp_7_share\\Results\\Traditional_Analysis\\MS_cross_taskeffect_wide_w_scale.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)
colnames(tmp) == colnames(crossf_effect_scale_1)
colnames(tmp)[colnames(tmp) == 'Sex'] <- 'Gender'
tmp <- tmp[,colnames(crossf_effect_scale_1)]
new_tmp <- rbind(crossf_effect_scale_1,tmp)
# write files to an upper-level folder
setwd(traDir)
write.csv(new_tmp,'MS_effect_w_scales_all.csv',row.names = F)
setwd(curDir)
```
